Carbonate chemistry at Ny-Ålesund

### 2021-04-14 awipev-CO2.Rmd
On the way

## Stratification
```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
# we look at the distribution of data
tmp <- d_all %>% 
  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
  group_by(month)

@@

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2_old <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(pco2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, pco2_air)

# downloaded 2021-04-14
# http://ebas.nilu.no/Pages/DataSetList.aspx?key=3673A72690B343B1AEC0F1673FE8C09D
file_names <- c("atmospheric_co2_zeppelin/NO0042G.20160101000000.20180420115103.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20170101000000.20180413180000.online_crds.carbon_dioxide.air.7mo.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", 
"atmospheric_co2_zeppelin/NO0042G.20180101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20190101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20200101000000.20210413000000.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas")
atm_co2 <- NULL
year_co2 <- ymd_hm(paste0(c(2016:2020), "-01-01 00:00"))
for (i in 1:5) {
print(i)
tmp <-
  read_table2(file = paste0(path, file_names[i]),
  comment = "#",
  #skip = 182,
  col_names = FALSE,
  na = c("9999.999", "99.999", "9999.990", "9999.99"),
  ) %>%
  dplyr::mutate(pco2_air = X3,
  datetime = year_co2[i] + X1*24*3600) %>% 
  dplyr::select(datetime, pco2_air)
  tmp$datetime <- lubridate::round_date(tmp$datetime, unit="1 minutes")
atm_co2 <- bind_rows(atm_co2, tmp)
  }

#d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
p_atm_co2 <- ggplot(data=atm_co2) +
  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```

>>>>

## Stratification
```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
# we look at the distribution of data
tmp <- d_hour %>% 
  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
  dplyr::mutate(month=month(d_hour$date, label = TRUE)) %>% 
  group_by(month)

@@

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2 <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(pco2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, pco2_air)
d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
p_atm_co2 <- ggplot(data=atm_co2) +
  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```
